Evaluating the Performance and Energy Efficiency of the COSMO-ART model system

### 2014-04-25 paper_enahpc14/Sec3:Environment-setup.tex
Manuel's changes

\item \textsc{Tintorrum} is  a heterogeneous cluster composed of
  28 compute nodes at UJI. For our  experiments only a subset of 16 homogeneous nodes was considered. Each of nodes of this subset includes a dual-socket hexa-core Intel Xeon E5645 processors 
  running at 2.40\,GHz, equipped with 288\,GB  of DDR3 1333\,MHz and connected via Infiniband QDR with a Mellanox MTS3600 switch. A  full tracing  experiment is  conducted on
  \textsc{Tintorrum} in order to  capture an overall  power profile at a much
  finer resolution. Also we analize the contribution of the MPI library
  to the energy consumption and how the use of the blocking versus polling
  message-passing policies can potentially render energy savings.
\end{itemize}

>>>>

\item \textsc{Tintorrum} is  a heterogeneous cluster composed of
  28 compute nodes at UJI. For our  experiments only a subset of 16 homogeneous nodes was considered. Each of them is composed dual-socket Intel Xeon E5645 hexa-core processors 
  running at 2.40\,GHz, equipped with 288\,GB  of DDR3 1333\,MHz and connected via Infiniband QDR with a Mellanox MTS3600 switch. A  full tracing  experiment is  conducted on
  \textsc{Tintorrum} in order to  capture an overall  power profile at a much
  finer resolution. In this sense, we also analyze the contribution of the MPI library
  to the energy consumption and how the use of the blocking versus polling
  message-passing policies can potentially render energy savings.
\end{itemize}
